\documentclass[10pt]{article}
\usepackage{amsmath, amssymb, geometry, setspace, booktabs}
\geometry{margin=0.6in}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=blue}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=1.5em}
\setstretch{1.15}

% Title page
\title{Brokerage Culture}
\author{Zheng Gong}
\date{\today}

\begin{document}
\maketitle
\thispagestyle{empty}
\begin{center}
    \rule{0.8\textwidth}{0.4pt}
\end{center}
\vspace{1em}

%\tableofcontents
%\newpage

\section{Prompts}

You are analyzing an analyst question asked during a company earnings call. Your task is to assess the question across five cultural dimensions associated with the analyst’s employer (the brokerage firm), based only on the text of the question.

Evaluate the question on the following dimensions. For each dimension, provide:
\begin{itemize}
\item A score from 1 (very weak) to 5 (very strong)
\item A brief justification for the score
\end{itemize}

The five cultural dimensions are:

\begin{itemize}
\item \textbf{Innovation} — Does the question reflect forward thinking, creativity, or a novel approach to analysis?
\item \textbf{Integrity} — Does it seek transparency, challenge vague or evasive answers, or emphasize ethical concerns?
\item \textbf{Quality} — Is it precise, well-structured, and focused on operational excellence or customer satisfaction?
\item \textbf{Respect} — Is the tone professional, considerate, and reflective of mutual respect?
\item \textbf{Teamwork} — Does the question reference collaboration, consensus, shared goals, or coordination?
\end{itemize}

\textbf{Analyst Question:} is below


\section{Results}

% Main content starts here
\input{table.tex}    


\input{table_by_year.tex}

\end{document}